Turbulence in compact to giant HII regions

### 2021-12-29 Corr.tex
Javier changes 2021-12-29

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:Reg}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &             log $R$ &   0.691$\pm$0.079 &   -0.85$\pm$0.148 &   0.984 &    <10\(^{-5}\) \\
 log $\sigma$ &            log L(H) &   0.166$\pm$0.129 &  -5.698$\pm$5.002 &    0.64 &  0.06 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &    0.749$\pm$0.62 &  -0.132$\pm$0.729 &   0.575 &  0.10 \\
 log $\sigma$ &         log $r_{0}$ &   0.195$\pm$0.207 &   0.679$\pm$0.139 &   0.493 &  0.17 \\
      log $m$ &            log Dist &   -0.07$\pm$0.091 &   1.113$\pm$0.185 &  -0.436 &  0.24 \\
      log $m$ &         log $r_{0}$ &  -0.031$\pm$0.086 &  -0.001$\pm$0.059 &  -0.295 &  0.44 \\
      log $m$ &        log $\sigma$ &  -0.094$\pm$0.264 &   0.061$\pm$0.204 &  -0.241 &  0.53 \\
\hline
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:Reg}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &             log $R$ &   0.684$\pm$0.068 &   -0.83$\pm$0.123 &   0.983 &    0.0 \\
 log $\sigma$ &            log L(H) &   0.175$\pm$0.095 &  -6.039$\pm$3.673 &   0.716 &   0.02 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.813$\pm$0.475 &  -0.208$\pm$0.543 &   0.668 &  0.035 \\
      log $m$ &            log Dist &  -0.111$\pm$0.081 &   1.209$\pm$0.155 &  -0.592 &  0.072 \\
 log $\sigma$ &         log $r_{0}$ &   0.221$\pm$0.182 &    0.65$\pm$0.122 &   0.545 &  0.103 \\
      log $m$ &        log $\sigma$ &  -0.142$\pm$0.237 &    0.106$\pm$0.18 &  -0.421 &  0.226 \\
      log $m$ &         log $r_{0}$ &  -0.046$\pm$0.084 &   0.015$\pm$0.055 &  -0.387 &  0.269 \\
\hline
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

### 2021-12-29 extrastuff.tex
Javier changes 2021-11-26
Javier changes 2021-12-29

@@

>>>>

We use data from \citet{1987A&A...176..347H} and \citep{arthur2016turbulence} to study of turbulence in the Orion Nebula.
\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used having the étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

@@

%The analysis employed until now is not conclusive about the true velocity fluctuations observed in each nebula. 
%As pointed out by \citet{arthur2016turbulence} other techniques also allow us to study these fluctuations.

### 2021-12-29 strucfunc_paper.tex
Javier changes 2021-12-17
Javier changes 2021-12-29

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  To characterize these fluctuations we apply a statistical analysis using the second-order structure function to archival \halpha\ observations of a diverse sample of 9 \hii{} regions.
  This regions are located in the Milky Way and other Local Group galaxies, and
  span more than two orders of magnitude in size and luminosity.
  We propose a functional form of the structure function that considers observational constraints.
  By using a chi-square analysis fitting this functional to our results we extract three parameters related to the fluctuations in the velocity field in each region. 
  The true velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
  autocorrelation length \(r_0\) covering to 0.06 - 8 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.3.
  The velocity dispersion is found to correlate primarily with luminosity and the autocorrelation length correlates primarily with the size of the region.
  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
  We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
\end{abstract}

@@

\begin{equation}\label{eq:functional}
B(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}

@@

The final form of our proposed functional of the structure function is in the form:
%
\begin{equation}\label{eq:fff}
B(r) = b(r; \beta r_0, \beta m) \times S(r; s_0, r_0) + B_{\text{noise}}
\end{equation}

@@

@@

\textit{Will 2021-12-10: Moving this section to later for now. Maybe
  this material could go in discussion}

@@

\subsection{Data}

\begin{figure*}
 \centering
 \includegraphics[width=5in]{Figures/Hist/Hist}\par
 \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
 \label{fig:hist}
\end{figure*}

@@

@@

@@

This line of investigation is followed using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
We use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p \leq $0.10.
In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.

The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region. The relationship we found is relation of $\log r_0 = (0.69 \pm 0.07) \log R-(0.85 \pm 0.14)$.

The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.16 \pm 0.12) \log \text{L}(\text{H}_{\alpha})-(5.6 \pm 5.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.32\pm 1.89) \log \sigma -(36.23 \pm 1.45)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)

@@

The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.75 \pm 0.60) \log \sigma_{\text{LOS}}-(0.13 \pm 0.70)$ .

@@

In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for determining the correlation length and the index of the slope. Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), the results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.

@@

Based on observations made with KPNO telescopes
\textit{complete KPNO acknowledgment}.
Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
Based on observations made as part of the Gaia-ESO Spectroscopic Survey
\textit{complete Gaia-ESO acknowledgment}.
Based on observations made with the WHT
\textit{complete WHT acknowledgment}.
JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.

@@

@@

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
  \end{tabular}
  \caption{Effects of finite box size on the structure function.
    (a)~Construction of simulated turbulent velocity fields of different sizes
    by repeated division of an initial field of size \(512 \times 512\) pixels.
    The \(j\)th level of division yields \(N = 4^j\) fields,
    each of linear size \(L \times L\) where \(L = 2^{9 - j}\). 
    (b)~Resultant structure functions.
  }
  \label{fig:finite-box}
\end{figure}

@@

>>>>

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  To characterize these fluctuations we apply a statistical analysis using the second-order structure function to archival \halpha\ observations of a diverse sample of 9 \hii{} regions.
  This regions are located in the Milky Way and other Local Group galaxies, and
  span more than two orders of magnitude in size and luminosity.
  We propose a functional form of the structure function that considers observational constraints.
  By using a chi-square analysis fitting this functional to our results we extract three parameters related to the fluctuations in the velocity field in each region. 
  The true velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
  autocorrelation length \(r_0\) covering to 0.06 - 8 pc, and the power-law slope \(m\) of the velocity field, which ranges from 0.7 to 1.5.
  The velocity dispersion is found to correlate primarily with luminosity and the autocorrelation length correlates primarily with the size of the region.
  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is roughly the double for all regions.
  We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
\end{abstract}

@@

\begin{equation}\label{eq:functional}
b(r; r_0, \sigma^2, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}

@@

The final form of our proposed functional of the structure function is in the form:
%
\begin{equation}\label{eq:fff}
B(r) = b(r; \beta r_0, \beta \sigma^2,m) \times S(r; s_0, r_0) + B_{\text{noise}}
\end{equation}

@@

\subsection{Velocity fields of the HII regions}

\textit{Javier 2021-12-28: I'm not quite sure the correct section for this. Since they aren't results, per se, and until now I haven't develop to much discussion with them, I move it here so it end up like Methods and Data, before reporting our findings. }

\begin{figure*}
 \centering
 \includegraphics[width=5in]{Figures/Hist}\par
 \caption{Histograms of the centroid velocities in \halpha\ of our sample of HII regions. }
 \label{fig:hist}
\end{figure*}

@@

\textit{Will 2021-12-10: Moving this section to later for now. Maybe
  this material could go in discussion. Javier 2021-12-28: In deciding the correct place for this part, if we ended up including it, I moved it to the results section. For now it makes sense to me because it is where the physical interpretation of the power law and the correlation length are presented for later report the results of each region.}

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\linewidth]{Figures/strucfunc-fit-D}
  \caption{Second-order structure functions for the velocity centroid images of the \(H\alpha\) emission line}\label{fig:strucfunc-fit-D}
\end{figure*}

@@

In the section \ref{sec:results} we showed that each HII region has a turbulent velocity field that can be characterized using the turbulence theory.
The turbulent parameters obtained are unique to each velocity field.
We proceed to develop scaling relations between them and between the physical properties of each region.
We also do a comparison between our results with previous structure functions.

@@

We follow through this analysis using the scaling relation as a research tool between the properties of the sample of HII regions and our results. 
We use the properties in Table \ref{tab:Reg} with the turbulent parameters in Table \ref{tab:Res} as the dependent variable to adjust a fit in the form $Y = aX +b$. 
For this procedure we use a hierarchical Bayesian approach using the package \textit{linmix} \citep{2007ApJ...665.1489K}.
The results are shown in Table \ref{tab:RestStats} in ascending order for the p-value.
In the Figures \ref{fig:rvsR}-\ref{fig:svss} we show the correlations with a significance level  $p < $0.05.
In all the figures the slope of the fit shown in solid black line is the mean of all red lines that reflect the posterior of the Bayessian analysis.

The Figure \ref{fig:rvsR} shows the strongest correlation, being this between the correlation length $r_0$ and the size $R$ of the region. The relationship we found is relation of $\log r_0 = (0.68 \pm 0.06) \log R-(0.83 \pm 0.12)$.

The Figure \ref{fig:sigvsl} shows the log $\sigma$-log $\text{L}(\text{H}_{\alpha})$ plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of $\log \sigma = (0.17 \pm 0.1) \log \text{L}(\text{H}_{\alpha})-(6 \pm 4.0)$.
It is customary in the literature to present $\text{L} (\text{H}_{\alpha})$ as the dependent variable.
In our case if we choose the upper positive error and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.5}\). 
Using the same procedure in \textit{linmix} and changing the variables we obtained $\log \text{L}(\text{H}_{\alpha}) = (3.2\pm 2) \log \sigma -(36.23 \pm 1.45)$.
Both relations are close to the previously proposed \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4}\)

@@

The Figure \ref{fig:svss} shows the log $\sigma$-log $\sigma_{\text{LOS}}$ plane with a relationship of $\log \sigma = (0.81 \pm 0.47) \log \sigma_{\text{LOS}}-(0.2 \pm 0.54)$ .

@@

In Section \ref{sec:apply} we mentioned the reduced chi-square method we are using for the determination of the correlation length and the index of the slope. Since this is the first time this method is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{2019arXiv191203543M}.

@@

Based on observations made with KPNO telescopes
\textit{complete KPNO acknowledgment}.
Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
Based on observations made as part of the Gaia-ESO Spectroscopic Survey
\textit{complete Gaia-ESO acknowledgment}.
Based on observations made with the WHT
\textit{complete WHT acknowledgment}.
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
JGV acknowledges and thanks CONACyT-Mexico for the PhD research scholarship.

@@

For a correct analysis on the structure function it is necessary to consider the consequences that the observational box size and the seeing have on the results.
To quantify the impact of these considerations on the final structure function, we perform a series of experiments using artificial turbulent velocity maps.
In particular, our interest is to quantify how this observational limitations affect the determination of parameters such as the correlation length, \(r_0\), and the velocity field variance, \(\sigma^2 \).

The artificial velocity maps are created using a modified version of the \textit{make$\_$extend} command from the \textit{turbustat} package \citep{Koch2019AJ....158....1K}.
We create a turbulent velocity field that follows a given power law with and a proposed correlation length, and a variance value indicated as true \(\sigma^2\).
Using this true \(\sigma^2\) we obtained the true \(r_0\), and these values are used as a reference in the following experiments to quantify the variations.
The objective is to create a sample of multiple divided maps with different seeing width to compute the structure function in each and characterize the variations.

@@

The Figure \ref{fig:finite-box}a shows some of the simulated velocity fields we use to study the variations in the structure function with respect to the size of the observational box.
Initially we have an original field of \(512 \times 512 \) pixels that are divided \(n\) times and produce \(N = 4^n\) fields, where each one has a linear size \(L \times L \) with \(L = 2^{9 -n}\).
The structure function is calculated for each division and later we average all the divisions of the corresponding map.

The Figure \ref{fig:finite-box}b shows in solid lines the normalized averaged structure functions for the maps in Figure \ref{fig:finite-box}a.
The number \(N\) of divisions and the length \(L\) are indicated in each structure function.
The shaded areas show the deviation that each average structure function has due to the different divisions. 
\textit{(Note: I modified the Figure adding \(\sigma^2\) and \(r_0\) for each SF since I think it is easier and more directly to grasp the effect of reducing the box size. The figure is more 'noisy' but if it seems like it contribute to nothing we can change it back.)}

The blue horizontal and vertical dashed lines show the true \(r_{0}\) and the value of \(\text{B}(r) / \sigma^2 = 1 \), respectively.
The colored dotted lines indicate the averages, taking into account all the divisions of each map, of the apparent \(r_ {0}\) and the apparent \(\sigma^2 \).
From this analysis it is clear that \(r_0\) and \(\sigma^ 2 \) decrease with respect to the true values as the size \(L\) of the observational box decreases. 
This analysis is performed on different maps (no images are shown) given a different power law in the velocity spectrum and different correlation lengths, giving the same results.

Figure \ref{fig:finite-box-effect} shows the ratio of the correlation length of each averaged map with respect to the true correlation length, \(\text{apparent } r_ 0 /\text{true } r_0 \), as well as the ratio between the averaged variance of each divided map and the true variance, \(\text{apparent } \sigma^2  / \text{true } \sigma^2\).
We observe that for the values where \(L\), is 20 $> r_0 $ the change in the ratios is null.
It is for the values where \( L < 10 r_0 \) a considerable decrease in both ratios is observed.
This behavior is fulfilled for all simulated maps with different power law in the velocity spectrum and different correlation functions, indicated with different colored circles in Figure \ref{fig:finite-box-effect}. 
These variations of the ratios are used to characterize the effect that the decrease of the observational box size has in \(r_0\) and \(\sigma^2\).

The fitted dashed line in Figure \ref{fig:finite-box-effect} is given by the equation:

\begin{equation}\label{eq:ajustebox}
\beta(r_0) = 1 - exp \left[ \frac{L}{3.6r_0} \right] 
\end{equation}
%
and it is used in the functional form that fits the observational structure function when adjusting the results to obtain the reported parameters \(r_0\) and \(\sigma^2 \).

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc2}
  \end{tabular}
  \caption{Effects of finite box size on the structure function.
    (a)~Construction of simulated turbulent velocity fields of different sizes
    by repeated division of an initial field of size \(512 \times 512\) pixels.
    The \(j\)th level of division yields \(N = 4^j\) fields,
    each of linear size \(L \times L\) where \(L = 2^{9 - j}\). 
    (b)~Resultant structure functions.
  }
  \label{fig:finite-box}
\end{figure}

@@

Ground-based astronomical observations are affected by the seeing produced by the atmosphere.
When calculating the structure function of these observations, this seeing affects the results at small-scale separations due to the smoothing of velocity fluctuations between adjacent pixels.
To study the consequences of the seeing we calculate the structure function of velocity maps where an artificial Gaussian seeing with different line widths has been introduced.
The artificial velocity maps are created in the same way as to study the effect of the observational box.
Seeing in velocity maps is added via the \textit{astropy} package using the \textit{Gaussian2DKernel} command.

The rows in Figure \ref{fig:seeing-reduction}a show a synthetic velocity field of 512 \(\times\) 512 divided into four maps of 256 \(\times \) 256.
The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
A Gaussian seeing, \(s_0 \) is applied to each division, with an RMS width ranging from 1 to 32 pixels, shown in the columns of Figure \ref{fig:seeing-reduction}. 
The structure function is computed in these maps and the averaged considering the same seeing.

The solid lines in Figure \ref{fig:seeing-reduction}b  show the ratio of the structure function of the averages of the maps with their respective seeing and the map without it: \(B (r, s_0 ) / B (r, s_0 = 0) \).
The circle symbols indicate the value of 2\(s_0\) while the plus symbols indicate the apparent correlation length of smoothed map.
The vertical dotted line indicates the true \(r_ {0} \).

The dashed lines in Figure \ref{fig:seeing-reduction}b are  empirically fits for each ratio.
To obtain this fit, we start from a convolution of an emission line and Gaussian seeing.
The emission line has the form \(\text {I}(x, v) = \text{I}_0 \phi [v; \overline {v} (x), \sigma_0]\) and has uniform width and brightness where the only change with respect to position is the velocity centroid.
The proposed seeing is \(\text{K}(x, s_0)\) of the form \(1 / \sqrt{2 \pi s_0} \exp^ {-x^ 2 / 2s_0 ^ 2} \).
The convolution \(\text{I}(x, v) \otimes \text{K}(x, s_0) \) is performed to obtain the smoothed map, \(\text {\~I} (x, v) \).

Then we calculate the average velocity difference of the original map, \(\Delta v \), and the smoothed map,b\(\tilde{\Delta v}\), in the points \( x = \{0, \delta \} \).
This expansion gives a term that modifies the final form of the structure function, \(\text{\~B} (r)\), where the structure function without the seeing, \(\text{B}(r) \), is corrected by the term \(S_0(r; s_0)\) which has the form:

\begin{equation}\label{eq:seeingcon}
S (r;s_0) = \tanh^2 \left[ \left( \dfrac{r}{2s_0} \right)^2 \right]
\end{equation}

Subsequently, the equation \ref{eq:seeingcon} is empirically modified and we obtain:

\begin{equation}\label{eq:seeingemp}
S(r; s_0, r_0) =  \frac{e^\frac{-s_0}{r_0}}{2} \left(1 + \tanh{a \text{ln} \frac{r}{2s_0}} \right)
\end{equation}
%
and the final form of the equation \ref{eq:seeingemp} after a mathematical simplification gives:

\begin{equation}\label{eq:seeingemp2}
S(r; s_0, r_0) = \frac{e^\frac{-s_0}{r_0}}{1+(\frac{2s_0}{r})^{2a}}
\end{equation}
%
which describes the fit (dashed lines) in Figure \ref{fig:seeing-reduction}b.

The equation \ref{eq:seeingemp2} is used to correct the observational structure function, \(\text{B}(r)\).
